Based on the main goal, the work present in the thesis resulted in three novel QoE prediction models.
These models are summarized as follows:


\begin{enumerate}
  \item A QoE prediction model, namely BiLSTM-QoE, is proposed for continuously predicting the user's QoE.
  The BiLSTM-QoE model utilizes Bidirectional Long Short-Term Memory networks to deal with the complex temporal dependencies in sequential QoE data.
  The evaluation results show that the BiLSTM-QoE model achieves promising performance in terms of accuracy compared with other referenced models.
  
  
  \item Despite the high accuracy of the BiLSTM-QoE model, the sequential processing characteristic in BiLSTM architecture increases the computational complexity of the model.
  Thus, the CNN-QoE model is presented to overcome the computational complexity drawbacks, while at the same time improve QoE prediction accuracy.
  Based on a comprehensive evaluation, the CNN-QoE model can provide a high QoE prediction performance that outperforms the existing approaches.
  
  
  \item The BiLSTM-QoE and CNN-QoE models focused on continuously predicting the instantaneous QoE which can provide the user's instant perceived video quality at a certain moment.
  However, in order to correctly determine the user's QoE for performing a QoE-based network control and management, it is necessary to produce a highly accurate QoE prediction either at any moment or at the end of a streaming session.
  Thus, the user's cumulative QoE can be potentially utilized as a better alternative than instantaneous QoE.
  The cumulative QoE is cumulatively estimated from the time when the viewer starts watching a streaming video content to any moment of the streaming session.
  A novel cumulative QoE prediction model is proposed that precisely assesses the user's cumulative perception.
  Moreover, in order to accurately model the user's cumulative QoE, the model also takes into account the human-related factors (i.e., memory effects, user's interest in the video content) which is not considered in the BiLSTM-QoE and CNN-QoE models.
  Evaluation results indicated that the model performs excellently in predicting cumulative QoE at any moment within a streaming session.
\end{enumerate}